### 2024-09-11 basic-statistics.qmd
20240911 - skewness and kurtosis

- mean
- median
- Hodges-Lehmann statistic (aka pseudomedian)
- mode
- weighted mean
- weighted median

@@

>>>>

- mean (aka "average")
- median
- Hodges-Lehmann statistic (aka pseudomedian)
- mode
- weighted mean
- weighted median

@@

Positive skewness (right-skewed) reflects a longer or heavier right-tailed distribution, whereas negative skewness (left-skewed) reflects a longer or heavier left-tailed distribution.
Fantasy points tend to be positively skewed.

The kurtosis reflects the extent of extreme (outlying) values in a distribution relative to a normal distribution (or bell curve).
A mesokurtic distribution (with a kurtosis value near zero) reflects a normal amount of tailedness.
Positive kurtosis values reflect a leptokurtic distribution, where there are lighter tails and a sharper peak than a normal distribution.
Negative kurtosis values reflect a platykurtic distribution, where there are heavier tails and a flatter peak than a normal distribution.
Fantasy points tend to have a leptokurtic distribution.
